Formula 1 2022 Regulation Changes

### 2024-04-21 paper/paper.qmd
added netherlands speed graphs

# Plotting
plot2 <- ggplot(filtered_data, aes(x = time, y = speed, color = season)) +
  geom_line() +
  labs(title = "Comparison of Speeds: 2021 vs 2022 at Final Corner",
       x = "Session Time (s)",
       y = "Speed (km/h)") +
  theme_minimal() +
  scale_color_manual(values = c("2021" = "red", "2022" = "blue"))+
  labs(tag = "B")

@@

# Plotting
plot2 <- ggplot(filtered_data, aes(x = time, y = speed, color = season)) +
  geom_line() +
  labs(title = "Comparison of Speeds: 2021 vs 2022 at Final Corner",
       x = "Session Time (s)",
       y = "Speed (km/h)") +
  theme_minimal() +
  scale_color_manual(values = c("2021" = "purple", "2022" = "gold"))+
  labs(tag = "B")

@@

# Plotting
plot2 <- ggplot(filtered_data, aes(x = time, y = speed, color = season)) +
  geom_line() +
  labs(title = "Comparison of Speeds: 2021 vs 2022 at Final Corner",
       x = "Session Time (s)",
       y = "Speed (km/h)") +
  theme_minimal() +
  scale_color_manual(values = c("2021" = "red", "2022" = "darkgreen"))+
  labs(tag = "B")

>>>>

# Plotting
plot2 <- ggplot(filtered_data, aes(x = time, y = speed, color = season)) +
  geom_line() +
  labs(title = "Comparison of Speeds: 2021 vs 2022 at Final Corner",
       x = "Session Time (s)",
       y = "Speed (km/h)") +
  theme_minimal() +
  scale_color_manual(values = c("2021" = "red", "2022" = "blue"))

@@

# Plotting
plot2 <- ggplot(filtered_data, aes(x = time, y = speed, color = season)) +
  geom_line() +
  labs(title = "Comparison of Speeds: 2021 vs 2022 at Final Corner",
       x = "Session Time (s)",
       y = "Speed (km/h)") +
  theme_minimal() +
  scale_color_manual(values = c("2021" = "purple", "2022" = "gold"))

@@

# Plotting
plot2 <- ggplot(filtered_data, aes(x = time, y = speed, color = season)) +
  geom_line() +
  labs(title = "Comparison of Speeds: 2021 vs 2022 at Final Corner",
       x = "Session Time (s)",
       y = "Speed (km/h)") +
  theme_minimal() +
  scale_color_manual(values = c("2021" = "red", "2022" = "darkgreen"))

```{r}
#| label: fig-verspeed-netherlands
#| fig-cap: Verstappen Speed Comparison - Qualifying Netherlands 2022 vs 2021
#| echo: false
#| warning: false
#| message: false

ver_telemetry_data_dutch_2022 <- read.csv("../data/raw_data/verstappen_telemetry_dutch.csv")
ver_telemetry_data_dutch_2021 <- read.csv("../data/raw_data/verstappen_telemetry_dutch_2021.csv")

# Assuming telemetry_data_2022 and telemetry_data_2021 are your datasets
ver_telemetry_data_dutch_2022$season <- "2022"
ver_telemetry_data_dutch_2021$season <- "2021"

# Combine the datasets
combined_data <- rbind(ver_telemetry_data_dutch_2022, ver_telemetry_data_dutch_2021)

filtered_data <- combined_data %>%
  filter(time >= 45 & time <= 60)

# Plotting
plot2 <- ggplot(filtered_data, aes(x = time, y = speed, color = season)) +
  geom_line() +
  labs(title = "Comparison of Speeds: 2021 vs 2022 at Turn 11 and 12",
       x = "Session Time (s)",
       y = "Speed (km/h)") +
  theme_minimal() +
  scale_color_manual(values = c("2021" = "red", "2022" = "blue"))

```{r}
#| label: fig-hamspeed-netherlands
#| fig-cap: Hamilton Speed Comparison - Qualifying Netherlands 2022 vs 2021
#| echo: false
#| warning: false
#| message: false

ham_telemetry_data_dutch_2022 <- read.csv("../data/raw_data/hamilton_telemetry_dutch.csv")
ham_telemetry_data_dutch_2021 <- read.csv("../data/raw_data/hamilton_telemetry_dutch_2021.csv")

# Assuming telemetry_data_2022 and telemetry_data_2021 are your datasets
ham_telemetry_data_dutch_2022$season <- "2022"
ham_telemetry_data_dutch_2021$season <- "2021"

# Combine the datasets
combined_data <- rbind(ham_telemetry_data_dutch_2022, ham_telemetry_data_dutch_2021)

filtered_data <- combined_data %>%
  filter(time >= 45 & time <= 60)

# Plotting
plot2 <- ggplot(filtered_data, aes(x = time, y = speed, color = season)) +
  geom_line() +
  labs(title = "Comparison of Speeds: 2021 vs 2022 at Turn 11 and 12",
       x = "Session Time (s)",
       y = "Speed (km/h)") +
  theme_minimal() +
  scale_color_manual(values = c("2021" = "purple", "2022" = "gold"))

```{r}
#| label: fig-lecspeed-netherlands
#| fig-cap: Leclerc Speed Comparison - Qualifying Netherlands 2022 vs 2021
#| echo: false
#| warning: false
#| message: false

lec_telemetry_data_dutch_2022 <- read.csv("../data/raw_data/leclerc_telemetry_dutch.csv")
lec_telemetry_data_dutch_2021 <- read.csv("../data/raw_data/leclerc_telemetry_dutch_2021.csv")

# Assuming telemetry_data_2022 and telemetry_data_2021 are your datasets
lec_telemetry_data_dutch_2022$season <- "2022"
lec_telemetry_data_dutch_2021$season <- "2021"

# Combine the datasets
combined_data <- rbind(lec_telemetry_data_dutch_2022, lec_telemetry_data_dutch_2021)

# Plotting
plot2 <- ggplot(filtered_data, aes(x = time, y = speed, color = season)) +
  geom_line() +
  labs(title = "Comparison of Speeds: 2021 vs 2022 at Turn 11 and 12",
       x = "Session Time (s)",
       y = "Speed (km/h)") +
  theme_minimal() +
  scale_color_manual(values = c("2021" = "red", "2022" = "darkgreen"))
